A Simple Minibatch Acceptance Test for MCMC

### 2016-06-15 nips_2016.tex
finish my revise Haoyu

@@

Similar as the Subsection~\ref{ssec:gaussians}, we use Figure~\ref{} to reveal the accuracy of our estimation of ${\rm std}(\Delta')$ and stability of $\rho/\sigma^3$.

@@

\subsection{Proof of Theorem~\ref{thm:efficiency}}\label{app:theory4}
From Berry-Esseen theorem, we know $|F_n(x) - \Phi(x)| \leq \frac{C\rho}{\sigma^3\sqrt{n}}$, where $\Phi()$ is the CDF of standard normal distribution.

>>>>

\begin{figure}[t]
    \centering
    \includegraphics[width=1\linewidth]{CI_v02.png}
    \caption{
    Histograms of ${\rm std}(\Delta')$, confidence interval of ${\rm std}(\Delta')$ (middle), along with $\rho / \sigma^3$ (right).
    }
    \label{fig:exp_3}
    %\vspace{-10pt}
\end{figure}

@@

Similar as the Subsection~\ref{ssec:gaussians}, we use Figure~\ref{fig:exp_3} to reveal the accuracy of our estimation of ${\rm std}(\Delta')$ and stability of $\rho/\sigma^3$.

@@

\subsection{Proof of Theorem~\ref{thm:efficiency}}\label{app:theory4}
Since only the $\frac{N}{nT}\sum_{i=1}^n \left(\log p(x_i|\theta') - \log p(x_i|\theta_t) \right)$ term brings randomness into $\Delta'$. Define $X_i = \frac{N}{T}\left(\log p(x_i|\theta') - \log p (x_i|theta_t) \right)$, $\tilde{X_i} = X_i - E(X_i)$, and $Y_n = \frac{\sum_{i=1}^n \tilde{X_i}}{n}$ (i.e. $Y_n$ is the $\Delta' - E(\Delta')$). From Berry-Esseen theorem, $|F_n(x) - \Phi(x)| \leq \frac{C\rho}{\sigma^3\sqrt{n}}$, where $\Phi()$ is the CDF of standard normal distribution, $F_n()$ is the CDF of $Y_n$, $C$ is the constant parameter which is below 0.4748, $\rho = E(|\tilde{X_i}|^3)$, and $\sigma^2 = E(\tilde{X_i}^2)$. Since $\Delta'$ is an unbiased estimator of $\Delta$, the CDFs between $\Delta'$ and $\Delta + X_{\rm norm}$ has the same max gap (i.e. $\frac{C\rho}{\sigma^3\sqrt{n}}$).

From Equation~\ref{eq:criteria}, we show we want to use $\Delta' + X_{\rm corr}$ to approximate $\Delta + X_{\rm norm} + X_{\rm corr}$. Since $|F_{\Delta'} - F_{\Delta + X_{\rm norm}}| \leq \frac{C\rho}{\sigma^3\sqrt{n}}$, for the worst case, assume $\exists \xi, ~{\rm s.t.} |f_{\Delta'}(\xi) - f_{\Delta + X_{\rm norm}} (\xi)| = \max_x |f_{\Delta'}(x) - f_{\Delta + X_{\rm norm}}(x)| \overset{\Delta}{=} \eta $, where $f()$ represents the PDF function. Because PDF of $X_{\rm corr}$ has the positive value and unit area, we have: 
\begin{align*} 
& |(f_{\Delta'}*f_{X_{\rm corr}})(\xi) - (f_{\Delta+X_{\rm norm}}*f_{X_{\rm corr}})(\xi)| \\
& = |\int_{-\infty}^{\infty}f_{\Delta'}(\xi-\tau)f_{X_{\rm corr}}(\tau)d\tau - \int_{-\infty}^{\infty}f_{\Delta + X_{\rm norm}} (\xi -\tau) f_{X_{\rm corr}} (\tau) d\tau| \\
& = |\int_{-\infty}^{\infty} (f_{\Delta'}(\xi-\tau) - f_{\Delta + X_{\rm norm}} (\xi -\tau)) f_{X_{\rm corr}} (\tau) d\tau| \\
& \leq \int_{-\infty}^{\infty} |f_{\Delta'}(\xi-\tau) - f_{\Delta + X_{\rm norm}} (\xi -\tau) |f_{X_{\rm corr}} (\tau) d\tau  \\
& \leq \int_{-\infty}^{\infty} \eta f_{X_{\rm corr}} (\tau) d\tau \leq \eta
\end{align*}

where ``*'' represents the convolution operation.

Thus, after convolution with $X_{\rm corr}$, the maximum gap between PDF of the $\Delta'$ and $\Delta + X_{\rm norm}$ decreases. Thus, $|F_{\Delta' + X_{\rm corr}} - F_{\Delta + X_{\rm norm} + X_{\rm corr}}| \leq |F_{\Delta'} - F_{\Delta + X_{\rm norm}}| \leq \frac{C\rho}{\sigma^3\sqrt{n}}$. Thus, $|P_a - P_a'| = |\Pr (\Delta + X_{\rm norm} + X_{\rm corr} > 0) - \Pr (\Delta' + X_{\rm corr} > 0)|=|F_{\Delta + X_{\rm norm} + X_{\rm corr}}(0) - F_{\Delta' + X_{\rm corr}}(0)| \leq \frac{C\rho}{\sigma^3\sqrt{n}}$. We can choose $n$ so that $\frac{C\rho}{\sigma^3\sqrt{n}} < \varepsilon$ to ensure $|P_a - P_a'| < \varepsilon$. Thus, the requirement for $n$ is $n \geq \frac{C^2\rho^2}{\sigma^6 \varepsilon^2}$.
